Prelim Outline

### 2019-07-29 outline.tex
cleaned preliminary work a lot based on CuO paper edits I just made. Need to cut 18 -> 13 pages. Planning 3, 6, 4 pages for intro, preliminary work, and proposed work. or 4, 5, 4, dunno

\paragraph{CuO: Introduction} As a first step towards developing accurate models for extended systems like solids using DMD, we constructed a many-body effective model for the CuO molecule which accurately describes the eigenstates and spectra seen in experiment up to 2eV above the ground state.

\paragraph{CuO: Methods} In order to fit a model using DMD we had to construct a low energy space (LES), choose a sampling scheme for states within the LES resulting in our sample space (SS), develop a basis which can accurately describe variations within the LES, identify and select descriptors built out of these basis elements, and appropriately fit the data from our SS onto our selected descriptors.

\paragraph{CuO: Results and Discussion} The resultant model from our analysis accurately describes the various eigenstates as measured in experiment up to 2eV, and is quantitatively and qualitatively more accurate than competing methods like density functional theory.

\paragraph{Hubbard: Preliminary results} Our preliminary calculations on the 2x2 half-filled 1-band Hubbard model map out the limiting behavior in the U-T model space by investigating the effectiveness of the single descriptor models. \textcolor{red}{Will be changed based on how far along we get with preliminary results.}

>>>>

\begin{enumerate}
\item Intro (no subsection)
\begin{itemize}
\item Our objective is to construct a model Hamiltonian for the low-energy electronic excitations of the CuO molecule.

\item We will construct such a low-energy Hamiltonian by downfolding the non-relativistic \textit{ab-initio} Hamiltonian subject to the Born-Oppenheimer approximation.

\item It is important to note that the approximations present in (eqref) will prevent our model Hamiltonian from describing effects like bond-length relaxation and spin-orbit splitting.

\item The following four sections are dedicated towards detailing the DMD procedure.
\end{itemize}

\item Sampling low-energy states
\begin{itemize}
\item Sampling low-energy states involves selecting an approximate low-energy space to work with and choosing a scheme for drawing wavefunctions from that space.

\item We suggest two criteria for selecting $\mathcal{LE}^\prime$ so that a model fit on it approximates the target model fit on $\mathcal{LE}$ accurately.

\item First, the approximate space should be able to capture most of the variation among states expected in $\mathcal{LE}$.

\item Second, $\mathcal{LE}^\prime$ should be as low in energy as possible.

\item The sampling scheme can introduce a sampling bias into the final regressed model, and must be carefully chosen.

\item In this work, we consider an approximate low-energy space of FN-DMC projected multi-Slater-Jastrow trial wave functions.

\item The first criteria above can be satisfied by selecting determinants which capture the low-energy variations seen in the CuO molecule.

\item We can capture these variations by using determinants resulting from independent symmetry-targeted unrestricted Kohn Sham (UKS) calculations.

\item Of these UKS determinants, only those which contribute to accurately describing the low-lying excitations of the molecule are selected.

\item The second criteria is met by the FN-DMC projection.

\item A shell sampling scheme was used to sample states from the selected approximate low-energy space.

\item Extra samples were drawn for regions of descriptor space with sparse sample density to ensure a uniform distribution of samples across the space.
\end{itemize}

\item Selecting candidate descriptors 
\begin{itemize}
\item We start by constructing a single particle basis which will be used to express second quantized candidate operators based on two criteria.
First, the basis elements should be localized, atomic-like, and mutually orthogonal.

\item Second, the trace of the FN-DMC 1-RDM evaluated on the single particle basis should approximately equal the total number of electrons in the system.

\item To satisfy the first criteria above, we construct a set of intrinsic atomic orbitals (IAOs) to use for our single particle basis.

\item We validate the quality of the IAO basis by evaluating the trace of the FN-DMC 1-RDM on the basis over our sampled data.

\item We select the following set of 1- and 2-body operators to construct our candidate descriptors based on our understanding of the low-energy excitations of the CuO molecule and our sampled states

\item The parantheses of \textbf{eqref} contain the full set of symmetry allowed 1-body operators within the Cu 3d, 4s and O 2p space

\item The operator $\hat{n}_{3d_\delta}$ is not included as it is linearly dependent on the rest of the occupation operators

\item Two 2-body interaction terms are also considered: a Hund's coupling between Cu 4s and 3d orbitals and a Cu 4s Coulomb repulsion
\end{itemize}

\item Fitting the effective Hamiltonian 
\begin{itemize}
\item {A direct attempt at fitting all eleven terms in \textbf{eqref} leads to a high goodness of fit but unexpectedly large coefficients for the fit model.}

\item {By studying the condition number (CN) associated with the fit we conclude the large coefficients are symptomatic of multicollinearity between our candidate descriptors.}

\item {Alleviation of this multicollinearity is necessary as we will be interested in inferences related to the coefficients of our final model.}

\item {We approach the fitting using a principal components regression (PCR) to reduce the impact of the multicollinearity among our candidate descriptors.}

\item {Before moving forwards with the PCR we discuss two quantities used in our principal component selection: the cumulative explained variance ratio (CEVR) and CN.}

\item {We conduct a PCA and select the nine highest ranked PCs to use in the PCR.}

\item {A model fit to these nine PCs maintains an excellent goodness of fit without serious multicollinearity.}

\item {An inverse PCA transformation is used to map the fit coefficients corresponding to the PC descriptors back into the original eleven coefficients of (eqref), resulting in our final model.}

\item {We conclude by validating our model using a k-folds cross validation scheme.}

\item {We conduct 100 independent 5-fold cross validation tests for our nine PC model and find no indication of overfitting.}
\end{itemize}

\item Solutions of effective Hamiltonian
\begin{itemize}
\item Solutions of our effective Hamiltonian are obtained by exact diagonalization.

\item Before making comparisons to experiment, it was necessary to assign molecular term symbols to the model eigenstates.

\item We constructed the molecular orbitals (MOs) used for state assignments by diagonalizing the 1-body part of the model Hamiltonian.

\item We briefly discuss the constructed MOs, beginning with the $\delta$ and $\pi$ symmetry orbitals.

\item The three $\sigma$ symmetry MOs do not follow a simple bonding, non-bonding, anti-bonding structure.

\item In Figure \ref{fig:ed} we present the energies and occupations on this MO basis of the lowest-lying model eigenstates.

\item The model eigenstates are assigned term symbols using these MO occupations and spin multiplicities.

\item Equipped with term symbols, we compare our model solutions to experiment and find excellent agreement in state ordering and energies.

\item Note that our model has a larger error in describing high-energy eigenstates of the CuO molecule than low-energy ones.

\item The model states also agree with recent theoretical calculations like UKS and CCSD(T).

\item We believe the overestimation of the $^2\Delta$ excitation energy in UKS arises from an inadequate relaxation of the $\sigma$ orbitals.

\item We end by discussing the existence of a low-energy $^2\Sigma^-$ state for the CuO molecule which has not been observed in photoelectron spectroscopy.
\end{itemize}
\end{enumerate}
